%% FRONTMATTER
\begin{frontmatter}

% generate title
\maketitle

\begin{abstract}
A new particle decaying to a pair of vector bosons was discovered in 2012 by the ATLAS and CMS experiments at the Large Hadron Collider. In the wake of this discovery a rush of measurements was made to characterize this particle. The four-lepton final state has been instrumental in both the discovery and characterization of this new particle. With only about 20 events seen in the resonance peak at $\unit{125}{\GeV}$ the CMS experiment has been able to make considerable progress in characterizing the Higgs-like boson using the wealth of information in this final state in concert with other decay modes. In addition to the search for this new boson we present three recent results in the study of the Higgs-like boson properties: studies of the production mode, total width, and spin-parity quantum numbers.

First we present the search for this new resonance using the $H \to ZZ \to 4\ell$ decay channel. Then we discuss the production mode measurement using this final state. Next, we present two results that provided breakthroughs in the study of the Higgs-like resonance. One is the measurement of the width from an interplay between the off-shell and on-shell production, setting a limit three orders of magnitude tighter than previous limits. The other is the tensor structure measurement of the bosons interactions with pairs of vector bosons, leading to constraints on its spin-parity properties, where only limited measurements had been done before. All of these results provide further confirmation that CMS has discovered a Higgs boson near $\unit{125}{\GeV}$.

\vspace{.3cm}
\noindent Primary Reader: Andrei Gritsan\\
Secondary Reader:

\end{abstract}

\begin{acknowledgement}

I would like to begin by thanking my research colleagues. This document and the science contained within are a testament to your will, brilliance, effort, and resolve. I consider myself luck to know and work with each and every one of you.

I would be remiss to begin this section by thanking anyone other than my advisor Andrei. I consider myself lucky to have worked with you these past years. You are a brilliant scientist with vision, insight, and determination. You are a great educator who gave me guidance, motivation, and knowledge. You are a fantastic leader instilling confidence, organization, and productivity.

Next I would like to thank my colleagues at JHU. Meng and Sara you have been amazing scientists, you have taught me so much and I want to thank you for your patience through this process. Ian, you have kept me sane and together we have produced an amazing set of results I wouldn't have made it without you. To the current and former graduate students, I would like to thank you for all of your help in making these studies a reality. I can only hope that I have helped you with your work half as much as you have helped me.

To my colleagues in CJLST working group, I have tried to say it many times but once more cannot hurt. I have benefitted greatly from the impeccable wheel that you have set in motion. It has been an uphill battle but at every turn we have met the call. I hope you understand the gratitude I have for your efforts.

To the CMS Higgs, HZZ, and Tracker Alignment working groups. I would like to thank you for for the discussions, support, arguments, guidance, and patience. The CMS collaboration is a large unwieldy group but together we have and will continue to produce amazing science and people.

I would also like to take an opportunity to thank the two professors who started me down this path Prof. Alice Bean from the University of Kansas and Prof. Tim Bolton from Kansas State University. Each of you have helped me begin this process and I hope that you know how happy I am that you did.

While this document presents the peak of my scientific and academic achievements to date I would also like to take some time to thank all of the people who me into a person capable of this work. I have had the great fortune of living with, working with, playing with, etc... some of the greatest people in the world. 

To all of my friends in Geneva who got me through two years away I want to say thanks and I hope to see you all again soon somewhere in this world. To all of my friends in Baltimore who helped me get through the difficult times with classes, exams, and medical emergencies I want to say thank you for supporting and working with me. To my friends from Zurich who opened my eyes to the world beyond my home, I would like to say thank you. To my friends from Lawrence I would like to thank you for all the laughs and stories. Finally to all of my friends in Manhattan, you helped shape me into who I am and I cannot come close to repaying you for that. To all of you whom I have leaned on and learned from, I would like to thank you!

Last I would like to take time to thank my family. I am so blessed to have such a large and loving family. As I began putting together the list of you to thank I realized that there were too many of you to list explicitly. Instead, I will have to address most of you in groups.

To my Martin family, I would like to thank you for all of the support and love. Specifically, Grandma and Grandpa have been such an important presence in my life that no words can repay. You are the glue that holds together one of the most loving and caring families that has ever existed. To my aunts, uncles, and cousins you have provided me with a wonderful family. Weather we are related by blood or experience, I want you all to know how I wouldn't trade our time together for anything.

To my Dysart family, I want to thank you for your encouragement and sacrifice. While I never got to know my Grandmother, based on your lives I assume that she was one of the most loving and caring people. You have shown me so much support and love that I cannot imagine her any other way. I also would like to thank you, and my Grandfather, for teaching me the value of sacrifice and community. I see in all of you, and saw in him, individuals who choose to do things for those around them ahead of themselves. For their immediate loved ones, or for wider groups of people, at every turn I see you looking to better everyones lives, not just your own.

To my Rice/McGinnity family, I would like to thank you for making me a part of your lives. I am so happy to have been adopted by such a wonderful group of people. I would like to thank you for giving me your support and guidance. I am so happy to see our family growing!

To my parents Susan Dysart-Martin and Randal Martin, thank you. I could try to put together a list of ways that you have helped me get to this point, but it would be woefully incomplete. Everything I am, I owe to you. For the support, encouragement, advice, drive, passion, everything thank you. None of this work could have happened without you. This is a testament to you as people and parents, thank you.

Finally I would like to thank my sister Layne Elizabeth Martin. You may not know or believe but you are my brightest inspiration. I still feel like an older brother who needs to prove to his younger sister that he can keep up with her. You are passionate, driven, caring and selfless. I am so lucky that you are in my corner and I will always be there for you.

\end{acknowledgement}

%\begin{dedication} 

%\end{dedication}

% generate table of contents
\tableofcontents

% generate list of tables
\listoftables

% generate list of figures
\listoffigures

\end{frontmatter}